\begin{rubric}{Work Experience}
% --- Entry 1: Metso ---
\entry*
    \textbf{Metso,} Frankfurt, Germany
    % ---  Role 1 ---    
    \par\vspace{0.5em}
	\textbf{Master Thesis} \hfill \textbf{11/2025 -- Present}
	\par \textbf{Topic:} Unsupervised Anomaly Detection on High-Dimensional Multivariate Industrial Time Series Data.
	\par Designed and benchmarked unsupervised anomaly detection models (PCA, Autoencoders, GDN, SimAD) on high-dimensional industrial sensor data.
	\par Developed an Adaptive PCA-based detection approach to handle concept drift and dynamic operating conditions in real-time process data.
    \par Performed extensive data preprocessing, feature engineering, and collaborated with process engineers and domain experts to qualitatively validate detected anomalies and reduce false positives.
    % ---  Role 2 ---
    \par\vspace{0.5em}
	\textbf{Data Scientist} \hfill \textbf{04/2025 -- 10/2025}
	\par Developed and productionized time-series outlier detection and forecasting models to support predictive maintenance use cases.
	\par Implemented CI/CD pipelines for model deployment and monitoring, and integrated MLflow for experiment tracking, model versioning, and performance comparison across multiple outlier detection approaches.
	\par Built real-time monitoring dashboards using Plotly and gRPC for live data streaming and outlier visualization.
    % ---  Role 3 ---
    \par\vspace{0.5em}
	\textbf{Data Science Intern} \hfill \textbf{10/2024 -- 03/2025}
	\par Conducted exploratory analysis on multivariate industrial time series data to identify sensor dependencies and abnormal patterns.
	\par Evaluated multiple forecasting and outlier detection techniques to assess feasibility for predictive maintenance.
	\par Built interactive visualization tools using Plotly to help engineers explore complex sensor relationships.
    \par Defined baseline data cleaning rules, KPIs, and validation strategies in collaboration with R\&D and domain experts.
    

% --- Entry 2: Dreamwarez  ---
\entry*
	\textbf{Dreamwarez,} Pune, India
    % --- Role 1 ---
	\par\vspace{0.5em}
	\textbf{Data Analyst} \hfill \textbf{08/2021 -- 02/2023}
	\par Designed and maintained PowerBI dashboards with DAX-based KPIs to support executive decision-making and operational insights.
	\par Performed data cleaning, transformation, and exploratory analysis using SQL, Pandas, and Python.
	\par Applied statistical analysis and machine learning techniques to uncover trends and patterns in structured and semi-structured datasets.
    \par Delivered data-driven insights to stakeholders, translating analytical results into actionable business recommendations.
    % --- Role 2 ---
    \par\vspace{0.5em}
	\textbf{Software Developer Intern} \hfill \textbf{02/2021 -- 07/2021}
	\par Developed user-centric web applications with a focus on data validation, backend stability, and responsive design.
	\par Collaborated in Agile/Scrum teams to implement features, debug issues, and optimize application performance.
    \par Built robust input validation pipelines to prevent invalid data ingestion and reduce backend processing errors.

\end{rubric}