\begin{rubric}{Projects}
\entry*
	\textbf{Document Intelligence Hub} \hfill \textbf{06/2025}
	\par Developed a RAG-based document intelligence system enabling semantic search and Q\&A over complex technical documents. 
    \par Implemented FAISS for efficient similarity search on document embeddings and FastAPI for real-time ingestion and inference.
    \par Designed modular pipelines for document parsing, embedding generation, and response synthesis.
\vspace{0.2em}
\entry*
	\textbf{E-Commerce Product Intelligence Engine} \hfill \textbf{03/2025}
	\par Built a product intelligence and recommendation system by transforming raw e-commerce data into vector embeddings.
    \par Enabled similarity-based product comparison and discovery using LLM-assisted retrieval techniques.
    \par Developed a modular web scraper and Streamlit application to support end-to-end data ingestion and analysis.
\vspace{0.2em}
\entry*
	\textbf{QuizCrafter AI} \hfill \textbf{01/2025}
	\par Developed an AI-driven quiz generation system producing context-aware MCQs and True/False questions using LLMs.
	\par Analyzed user performance trends using visual analytics to evaluate learning progress and question difficulty.
    \par Implemented strict output validation using Pydantic to ensure structured and reliable model responses.
\vspace{0.2em}
\entry*
	\textbf{Equity News Researcher Tool} \hfill \textbf{07/2024}
	\par Built a news retrieval system to support equity research by mapping user queries to relevant financial news articles.
	\par Applied embedding-based similarity search using FAISS to improve relevance and information discovery.
    \par Designed a Streamlit interface to enable interactive exploration of retrieved insights.
\vspace{0.2em}

% \entry*[]
% 	\textbf{T20 World-Cup Analytics Pro} \hfill \textbf{03/2024}
% 	\par Built an interactive PowerBI analytics dashboard to analyze T20 World Cup cricket data using 10,000+ scraped records.
% 	\par Implemented web scraping pipelines using Bright Data and performed data cleaning and transformation with Python and Pandas.
%     \par Designed DAX-based analytical measures to uncover performance trends, team comparisons, and player-level insights.
%
\entry*[]
	\textbf{Customer Churn Prediction} \hfill \textbf{01/2024}
	\par Conducted exploratory data analysis using plotly and data preprocessing using Pandas on customer data.
	\par Trained and evaluated multiple machine learning classification models to predict customer churn, achieving 91\% F1 score.
    \par Analyzed feature importance to identify key drivers of customer attrition and support retention strategies.
% %
% \entry*[]
% 	\textbf{Social Media Sentiment Analysis} \hfill \textbf{09/2023}
% 	\par Collected and processed social media data using Selenium and BeautifulSoup, followed by text cleaning with spaCy.
% 	\par Generated semantic representations using Word2Vec for downstream sentiment classification tasks.
%     \par Trained and compared machine learning classifiers, achieving 92.5\% accuracy using a Naive Bayes model.

\end{rubric}
